The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-11-27 paper/paper.qmd
update paper

library(arrow)
library(knitr)
library(rstanarm)
library(tidyverse)
library(ggplot2)
library(bayesplot)
library(ggridges)
library(broom.mixed)
library(kableExtra)
library(car)
library(loo)
library(modelsummary)
```

@@

@@

## Prediction
```{r}
#| echo: false
#| warning: false
analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
analysis_data_test <- read_parquet(here::here("data/02-analysis_data/test_data.parquet"))
factor_vars <- c("interview_conduct_method", "partner_interference", "child_interference",
                 "parent_interference", "relative_interference", "non_relative_interference",
                 "country", "interviewer_gender", "question_clarification", "respondent_reluctant",
                 "respondent_tried_best")

@@

# Import caret library and calculate confusion matrix
library(caret)

@@

# Print the confusion matrix
print(confusion_matrix)

scatter_data <- data.frame(
  Actual = analysis_data_test$respondent_understood_binary,
  Predicted = analysis_data_test$predicted_class
)

ggplot(scatter_data, aes(x = Actual, y = Predicted)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.5, color = "blue") +
  labs(
    title = "Scatter Plot of Actual vs Predicted Values",
    x = "Actual Response Understanding",
    y = "Predicted Response Understanding"
  ) +
  theme_minimal()

## Diagnostics
### Validation
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-diagnostic-checks
#| fig-cap: "Comparing Diagnostic Visualizations for Model Checking"
#| fig-subcap: ["Residual Histogram", "Pareto k Diagnostic Values"]
#| layout-ncol: 2

>>>>

library(arrow)
library(knitr)
library(rstanarm)
library(tidyverse)
library(ggplot2)
library(bayesplot)
library(ggridges)
library(broom.mixed)
library(kableExtra)
library(car)
library(loo)
library(modelsummary)
library(caret)
```

@@

- **caret** [@caret]: Provides a unified interface for training and tuning machine learning models, offering numerous functions for preprocessing data, feature selection, model training, and performance evaluation, which streamline the process of creating predictive models.

@@

## Prediction
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: tbl-comprehension-matrix
#| tbl-cap: "Confusion Matrix for Comprehension Classification"
#| tbl-subcap: ["Counts of Predictions vs Reference", "Performance Metrics Summary"]
#| layout-ncol: 2
analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
analysis_data_test <- read_parquet(here::here("data/02-analysis_data/test_data.parquet"))
factor_vars <- c("interview_conduct_method", "partner_interference", "child_interference",
                 "parent_interference", "relative_interference", "non_relative_interference",
                 "country", "interviewer_gender", "question_clarification", "respondent_reluctant",
                 "respondent_tried_best")

@@

@@

confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
                           dimnames = list("Prediction" = c("Not_understood", "Understood"),
                                           "Reference" = c("Not_understood", "Understood")))

# Extract True Positive, False Positive, True Negative, and False Negative from the confusion matrix
TP <- confusion_matrix["Not_understood", "Not_understood"]
FP <- confusion_matrix["Not_understood", "Understood"]
TN <- confusion_matrix["Understood", "Understood"]
FN <- confusion_matrix["Understood", "Not_understood"]

# Calculate evaluation metrics
accuracy <- (TP + TN) / sum(confusion_matrix)
precision <- TP / (TP + FP)
recall <- TP / (TP + FN)
specificity <- TN / (TN + FP)
fpr <- FP / (FP + TN) # False Positive Rate
fnr <- FN / (FN + TP) # False Negative Rate
f1_score <- 2 * (precision * recall) / (precision + recall)
balanced_accuracy <- (recall + specificity) / 2

# Create a data frame for metrics
metrics_df <- data.frame(
  Metric_Name = c("Accuracy", 
                  "Precision (Positive Predictive Value, PPV)",
                  "Recall (True Positive Rate, TPR)", 
                  "True Negative Rate (TNR, Specificity)", 
                  "False Positive Rate (FPR)", 
                  "False Negative Rate (FNR)", 
                  "F1 Score", 
                  "Balanced Accuracy"),
  Value = round(c(accuracy, precision, recall, specificity, fpr, fnr, f1_score, balanced_accuracy), 4)
)

# Print the metrics table
kable(metrics_df, caption = "Evaluation Metrics for Classification Model")

confusion_df <- as.data.frame(as.table(confusion_matrix))

confusion_df %>%
  kable("html", col.names = c("Reference", "Not_understood", "Understood"), 
        caption = "Confusion Matrix for Comprehension Classification") %>%
  kable_styling(full_width = FALSE)

```
@tbl-comprehension-matrix-2 presents the confusion matrix for the comprehension classification model. The matrix provides the counts of correct and incorrect classifications between the "Not_understood" and "Understood" categories, highlighting how well the model performed in predicting respondent comprehension. The diagonal elements represent the correctly classified observations, while the off-diagonal elements indicate misclassifications. The matrix helps visualize the strengths and weaknesses of the model, particularly in distinguishing between respondents who understood versus those who did not.

@tbl-comprehension-matrix-1 shows the evaluation metrics for the classification model. These metrics include Accuracy, Precision (Positive Predictive Value), Recall (True Positive Rate), True Negative Rate (Specificity), and F1 Score, among others. The metrics provide a comprehensive summary of the model's performance, measuring not only how many predictions were correct, but also evaluating the balance between sensitivity and specificity. The high specificity and overall accuracy indicate that the model is effective in identifying respondents who understood the questions, but the low recall suggests limitations in detecting those who did not understand.
## Diagnostics
### Validation
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-diagnostic-checks
#| fig-cap: "Comparing Diagnostic Visualizations for Model Checking"
#| fig-subcap: ["Residual Histogram", "Pareto k Diagnostic Values"]
#| layout-ncol: 2
